The work presented in this thesis would not have been possible without the large
contribution of many people around me. First of all, I would like to thank my
advisor, Alessandro Gozzi, for all the guidance during the past few years.
Working with him has been formative from personal, professional and scientific
perspectives and it has also been a great experience. Moreover, the group of
people that Alessandro brought together in the Functional Neuroimaging Lab will
be difficult to beat elsewhere. Alberto Galbusera, Alessia de Felice, Carola
Canella, Daniel Gutierrez Barragan, Ludovico Coletta and Marco Pagani are great
colleagues and great friends and I really enjoyed working with them. A special
shout-out goes to Alberto for collecting most of the MRI data that I have worked
with. I would also like to thank all past members of the lab and other
collaborators: Alice Bertero, Anna Aksiuto, Gergely David, Manuel Blesa, Nayome
Rey Calvo and Richard Gomolka.

Pursuing a PhD, while stressful and often full of struggle, has also been a lot
of fun, both inside the office and outside. I immensely enjoyed all the trips,
hikes and aperitivi with my colleagues and other friends from CIMeC, IIT and
around: Germ\'{a}n Kruszewski, Georgiana Dinu, Jan B\'{i}m, Nghia The Pham and
many, many others with whom I have been lucky to share the beautiful city of
Rovereto and the mountains around.

Many thanks go to the administration of the Doctoral School and the Center for
Neuroscience and Cognitive Systems, namely to Leah Mercanti, Sara Maistrelli and
Paola Battistoni, for making all the paperwork a (mostly) smooth ride. I would
also like to thank the members of my oversight committee, Stefano Panzeri and
Jorge Jovicich, for all the feedback they provided.

My parents, Hana and Zbyn\v{e}k, and my brothers, Jan and Martin, provided a
great amount of support over the past years. Their visits in Rovereto were
always a source of joy!

Finally and above all, I would like to thank Angeliki, whose encouragements,
laughs and support made the start of our journey extraordinary.
